---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Overview

`chemmodlab` contains a suite of methods for fitting machine learning models and for validating the resulting models:
    
* `ModelTrain()` fits a series of classification or regression models to sets of descriptors and computes cross-validated measures of model performance.  Repeated k-fold cross validation is performed with multiple, different fold assignments for the data ("splits").
* `MakeModelDefaults()` makes a list containing the default parameters for all models implemented in ModelTrain.
* `plot.chemmodlab()` takes a chemmodlab object output by the `ModelTrain` function and creates a series of accumulation curve plots for assesing model and descriptor set performance.
* `Performance()` can evaluate many performance measures across all splits created by `ModelTrain`, then outputs a data frame for each D-M combination.
* `CombineSplits()` evaluates a specified performance measure across all splits created by `ModelTrain` and conducts statistical tests to determine the best performing descriptor set and model (D-M) combinations.
* `chemmodlab()` is the constructor for the chemmodlab object.
    
    The statistical methodologies comprise
    a comprehensive collection of approaches whose validity and utility have
    been accepted by experts in the Cheminformatics field. As promising new
    methodologies emerge from the statistical and data-mining communities, they
    will be incorporated into the laboratory. These methods are aimed at discovering
    quantitative structure-activity relationships (QSARs). However, the user can
    directly input their own choices of descriptors and responses, so the capability
    for comparing models is effectively unlimited.
    
# Installation

```{r, eval = F}
# install from CRAN
install.packages("chemmodlab")

# Or use the development from GitHub:
# install.packages("devtools")
devtools::install_github("jrash/chemmodlab")
```

# Usage

```{r message=FALSE, warning=FALSE, results='hide'}
library(chemmodlab)

data(aid364)
cml <- ModelTrain(aid364, ids = TRUE, xcol.lengths = c(24, 147),
                  des.names = c("BurdenNumbers", "Pharmacophores"))
plot(cml, splits = 1, meths = c("NNet", "KNN"))
CombineSplits(cml, metric = "enhancement", m = 100)
```

